Covid-19 A Spatio-Temporal Investigation.

### 2021-01-09 Notebooks/paper_covid.rmd
Update paper_covid.rmd

 The statistical software R (Version 4.0.3) was used to calculate the spatial and the spatio-temporal association, the Covid-19 database used in the study is also available in R, in a package called "COVID19" built by the *COVID-19 Data Hub* $\!\!^1\!^0$, the database begins in January 2020 and is constantly updated, it also gathers data from various sources of information for all countries in which it was possible to obtain data. The database provides data about political measures adopted by each country during the pandemic, even though that information is not available for all countries included, which is one of the limitations of the database, that lack of data can also be seen in variables such as the number of recovered cases, where China for instance had no recovered cases during the analysis' period of time, since the reason for this was not explicit in the website of *COVID-19 Data Hub*, this paper supposes it was not possible to access data for countries which the information was lacking in the unified database.

 O número acumulado de mortes, casos confirmados e recuperados são disponibilizados pelo banco de dados da *COVID-19 Data Hub*, no entanto como apenas são disponibilizados a quantidade acumulada, foi necessário calcular a quantidade mensal, para cada uma das variáveis, dentre os meses de Janeiro a Outubro. No banco também é disponibilizada a quantidade de habitantes de cada país, portanto para melhor capturar o impacto do Covid-19 em cada localidade a quantidade de casos, recuperados e mortes foram calculadas de acordo com a razão pelo número de habitantes.

>>>>

 The statistical software R (Version 4.0.3) was used to calculate the spatial and the spatio-temporal association, the Covid-19 database used in the study is also available in R, in a package called "COVID19" built by the *COVID-19 Data Hub* $\!\!^1\!^0$, the database begins in January 2020 and is constantly updated, it also gathers data from various sources of information for all countries in which it was possible to obtain data. The database provides data about political measures adopted by each country during the pandemic, even though that information is not available for all countries included, which is one of the limitations of the database, that lack of data is also be seen in variables such as the number of recovered cases, where China for instance had no recovered cases during the analysis' period of time, since the reason for this was not explicit in the website of *COVID-19 Data Hub*, this paper supposes it was not possible to access data for countries which the information was lacking in the unified database.

 The cumulative number of deaths, infections and recovered cases is given by the database, but since these numbers are only available in its daily cumulative form, it was necessary to calculate monthly quantities for each one of the variables between January and December 2020. The population of each country is also available in the database, so in order to better understand the effects of Covid-19

 No banco também é disponibilizada a quantidade de habitantes de cada país, portanto para melhor capturar o impacto do Covid-19 em cada localidade a quantidade de casos, recuperados e mortes foram calculadas de acordo com a razão pelo número de habitantes.
